---
title: "Investigating Simultaneity"
author: "Jonas Björnerstedt"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    number_sections: yes
---

```{r setup, include=FALSE}
library(ggplot2)
square <- function(x) {
  x^2/2+x+1
}
```

> SimMarket linear parameter structure:
beta = [ 1, 0];
x = [5, 0];
x_vcv = [1, 1];
c = 4;
c_vcv = 1;
gamma = 0;
epsilon_sigma = .1;
sigma_xi = .1;
endog_sigma = 0.1; % Degree of corr between x and epsilon
prob_prod = .8;    % Prob of product existing in market    

> epsilon = endog_sigma + sigma_xi
eta = N( 0, c_vkv)

> x = N(model.x, model.x_vcv)
d = [x(2:end), 1] * beta' + epsilon

> w = N(0, 1)
c = modell.c + m

## Introduction

The purpose of this document is to 

1. Calculate how simultaneity affects bias of OLS estimates. Why is the bias
of OLS estimates so small in SimMarket?
1. Can regional markets to some extent identify endogenous relationships?

\begin{eqnarray*}
q & = & d-ap+e\\
p & = & c+mq+w
\end{eqnarray*}


Thus 

```{r logit, echo=FALSE}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(data.frame(x=c(0, 2)), aes(x)) + 
  stat_function(fun=square, colour="red") +
  stat_function(fun=exp, colour="blue") 
```


